\begin{rubric}{Work Experience}
\entry*[Dec 2022 -- Present]%
	\textbf{Python Machine Learning Developer} at Aks IQ \hfill\textbf{Karachi, PK}
        \par Used machine learning and pretrained Automatic Speech to Text models such as Whisper and Text to Speech models to create an intelligent transcript based video editor application. Deployed machine learning models for Hscode prediction. Built intelligent information retreival system for product descriptions.
\entry*[Jan 2023 -- Present]%
        \textbf{Teaching Assistant for Natural Language Processing Course} at Habib University \hfill\textbf{Karachi, PK}
        \par Provided support to the instructor by conducting weekly hours, tutoring sessions and designing and grading reading assignments.
\entry*[Dec 2022 -- Present]%
	\textbf{Virtual Machine Learning Intern} at Empathic Computing Lab (ECL) \hfill\textbf{Auckland, NZ}
        \par Cleaned and filtered EEG VR data and understood its relationship. Used machine learning and deep learning techniques to obtain and analyze neurophysiological measures of Working Memory and the Cognitive Pupillary Response on Memory Tasks. 
\entry*[Aug 2022 -- Dec 2022]%
        \textbf{Teaching Assistant for Nature of Computation Course} at Habib University \hfill\textbf{Karachi, PK}
        \par Provided support to the instructor by conducting weekly recitations and tutoring students in office hours on complexity and computatbility theory.
\entry*[May 2022 -- Sep 2022]%
	\textbf{Google Summer of Code 2022 Contributor} at COPASI.org, \hfill\textbf{Connecticut, US}
        \par Contributed to open-source development for Cloud COPASI under National Resource for Network Biology (NRNB) by developing a new version that allows users to gain predefined access to UConn's HPC without configuration.
    \entry*[Jun 2022 -- July 2022]%
	\textbf{Backend Intern} at Securiti.ai \hfill\textbf{Karachi, PK}
        \par Created algorithms to assist the content classification (cc) backend team to increase efficiency of the product. Developed
Logfile Analyzer using SVM model in python, Regex merger algorithm for one go postal code extraction and Powerpoint data extractor using Apache POI.
\entry*[Jan 2022 -- June 2022]%
	\textbf{Developer for Canvas LMS} at Habib University \hfill\textbf{Karachi, PK}
        \par Worked on an ed-tech project of creating a course files tool for automatic download of course contents and reports directly from Canvas LMS.
\entry*[Jul 2021 -- Aug 2021]%
	\textbf{Workshop Facilitator at Habib University} at Habib University \hfill\textbf{Karachi, PK}
        \par Facilitated and taught a 10-lecture intensive programming fundamentals workshop to incoming batch of students. 
\entry*[Jun 2021 -- Aug 2021]%
        \textbf{Information Security Intern} at Bank Islami Pakistan Limited  \hfill\textbf{Karachi, PK}
        \par Analyzed websites and applications, reported the vulnerabilities found in a formal way and hunted threats using SIEM IBMQradar.
\entry*[Jan 2021 -- May 2021]%
        \textbf{Teaching Assistant for Discrete Mathematics Course} at Habib University \hfill \textbf{Karachi, PK}
        \par \par Provided support to the instructor by conducting weekly recitations and tutoring students in office hours to build a strong mathematical and computer sciencefoundation.
\entry*[Jan 2021 -- May 2021]%
        \textbf{Teaching Assistant for Object Oriented Programming Course} at Habib University \hfill \textbf{Karachi, PK}
        \par \par Provided support to the instructor by conducting weekly recitations, grading labs and tutoring students in office hours on OOP concepts.
        
        
\end{rubric}